How to compute the fusion product of MV cycles in type A

### 2021-04-29 draft.tex
p14 to 16 revamped

On the one hand, if $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $, then $ g(A)$ is lower-triangular with diagonal $ t^{\mu'} (t-s)^{\mu''}$, and so $ g(A) \in N_-[t, t^{-1}, (t-s)^{-1}] t^{\mu'} (t-s)^{\mu''}$. 
\acom{not $g(A)\CC[t]^m$}
\jcom{This one isn't a point in $ \Gr$, the others I changed.}

On the other hand, if $ (g(A)\CC[t]^m, s) \in S^{\mu', \mu''}_{0,\AA}$, then we can write 
$$
    g t^\mu r= n t^{\mu'} (t-s)^{\mu''}
$$
for some $ r \in G(\CC[t]), n \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu''} t^{-\mu''}$ which lies in $ T_1(\Oinf) $. % was CC\xt[]
Note that $ h^{-1}n h \in N(\Kinf)$, 
% ((t^{-1}))
so we can factor it as $ h^{-1} n h  = n_1 n_2 $, where $ n_1 \in N_{-,1}(\Oinf), n_2 \in N_-(\CC[t])$.  So then after doing a bit of algebra, we reach
$$
    t^\mu r (t^{-\mu} n_2^{-1} t^\mu) t^{-\mu} = g^{-1} h n_1.
$$
Since $ g, h, n_1 \in G_1(\Oinf)$, the right hand side $ g^{-1} h n_1 $ lies in $ G_1(\Oinf) $.  Since $ \mu $ is dominant, $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$, and so the left hand side lies in $t^\mu G(\CC[t]) t^{-\mu}$.

Moreover, since $ \mu $ is dominant, we know that 
$$
    t^\mu G(\CC[t]) t^{-\mu} \cap G_1(\Oinf) = N_1(\Oinf)\,.
$$
% $$t^\mu G(\cO) t^{-\mu} \cap G_1(\CC\xt[t^{-1}]) = N_1(\CC\xt[t^{-1}]\,.$$
Thus, we deduce that $ g^{-1} h n_1 \in N_1(\Oinf)$ 
% $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ 
and hence $ g(A) \in t^{\mu'} (t-s)^{\mu''} N_1(\Oinf) $.  
% Given that we know that 
Since $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA}$ as desired.
\end{proof}
% 
\jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows). To make them correct we should either switch to having $ \mu$ being antidominant or switch $ N$ to $ N_-$.  In this proof $ g(A)$ generally denotes a group element, rather than an affine Grassmannian element which conflicts a bit with earlier usage.}
% 
%\acom{What was the answer to Roger's question why is $g^{-1}hn_1 \in G_1 (\Oinf)$}
% 
%\rcom{So if we look at $g = g(A)t^{-\mu}$, since $A \in \TT_\mu$, the entries of $g(A)_{ij}$ are polynomials of degree $\min(\mu_i-1,\mu_j-1)$ when $i \neq j$, otherwise of degree $\mu_i$. When we multiply by $t^{-\mu}$, we scale the $i$th column by $t^{-\mu_i}$. So the diagonal entries are $1 + p$ where $p \in t^{-1}\CC[t^{-1}]$ while the off-diagonal entries in column $i$ have highest (in $t$) degree $\min(\mu_i-1, \mu_j-1) - \mu_i < 0$. Hence $g \in G_1(\cO_\infty)$.}
% 
Restricting to the zero fibre we recover \cite[a main result]{dthesis}, itself a corollary of the ordinary affine Grassmannian version of \Cref{th:OGrl}, \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}. \acom{Technically the zero fibre is comprised of $\CC[t]$ lattices and we need to `specialize' to end up in the ordinary $\Gr$.}
% 
\begin{corollary}
    \label{cor:mvy}
    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu$. 
\end{corollary}

\section{Falling Action} % Resolution
\acom{Recall (from optional \Cref{s:exposition}) the question motivating this work --- Roger's thesis, cluster monomials and the MV basis. Clarify that whereas we have so far only seen spaces related to ``ordinary MV cycles'' it is the ``stable MV cycles'' that are used to define the MV basis of $\CC[N]$ that the motivating question is concerned with. This discrepancy is the reason we might want to discuss maps $B(\infty)\to B(\lambda)$.}
% 
\begin{comment}
\begin{theorem}
    Let $\lambda_i\ge\mu_i$ be dominant ($i=1,2$), $\mu = \mu' +\mu''$, and $\lambda =\lambda'+\lambda''$. 
    % I have an irrational dislike of ending sentences with subscripts --- can we fix this?
    There is an isomorphism 
    \begin{equation}
        \overline{\OO}_{\lambda',\lambda''}\cap\TT_{\mu',\mu''} \to \overline\Gr_\AA^{\lambda',\lambda''}\cap \cW_{\mu',\mu''}
    \end{equation}
    got by taking a $\mu\times\mu$ block matrix $A$ in the $s$-fibre $\overline{\OO_{\lambda',\lambda''}^s}\cap\TT_{\mu',\mu''}^s$ on the left to the representative of the $s$-fibre on the right defined by  
    \begin{equation}
        \begin{split}
            g &= t^{\mu'} (t-s)^{\mu''} + a(t) \\
            a_{ij}(t) &= - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1}
        \end{split}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
\end{theorem}

@@

\begin{proof}
    % Copy Roger's proof.
    We have
\[
\begin{split}
    S_{\mu_1, \mu_2} & = N\xT[t^{-1}]t^{\mu_1}(t-s)^{\mu_2} \\
     & \subset T_1\xt[t^{-1}] N\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = T_1\xt[t^{-1}] N_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \qquad \text{\cite[Lemma 2.3]{kamnitzer2014yangians}}\\
     & = B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & \subset G_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & = W_{\mu_1 + \mu_2}
\end{split}
\]
where $B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2}$ since 
\[
\frac{t}{t-s} = 
1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
\in B_1\xt[t^{-1}].
\]
\end{proof}
\end{comment}
% 
We begin this section with some new notation. Let $YT(\lambda)_\mu$ denote the set of (possibly semistandard) Young tableaux of (arbitrary) shape $\lambda$ and (arbitrary) weight $\mu$. Here, the weight of a tableau is a sequence $(\mu_1,\mu_2,\dots)$ recording the number of boxes of weight $i = 1,2,\dots$ that the tableau contains, and the weight of a box is just the number that the box contains.
% For the sake of making a definition, we momentarily put some letters of our alphabet in unexpected roles, and ask you to suspend your disbelief. Given an arbitrary tableau $t$ having weight $w$ and shape $s$, we denote by $s(i)$ (resp.\ $w(i)$) the shape (resp.\ the weight) of $t(i)$, the tableau got from $t$ by discarding all boxes of weight exceeding $i$.

Given $\tau\in YT(\lambda)_\mu$ we denote by $\lambda(i)$ (resp.\ $\mu(i)$) the shape (resp.\ the weight) of $\tau(i)$, the tableau got from $\tau$ by discarding all boxes of weight exceeding $i$.

Given $A \in M_N(\CC)$ we denote by 
% $A\big|_{\CC^i}$ 
$A\big|_{\CC^p}$ 
the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors. If $A\big|_{\CC^p}$ preserves $\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$.

The variety $X(\tau)$ defined by
% from $\tau\in YT(\lambda)_\mu$ by 
\[
X(\tau) = \overline{
    \{
        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
    \}
}    
\]
is called a \textbf{generalized orbital variety}. 
% 
It inherits a crystal datum called a \textbf{Lusztig datum} from its tableau. 
\acom{Cite Joel? Hide dependence on reduced expression?}
The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is got from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ \acom{cite BZ} by the formula 
$$
n_\bullet(\tau)_{i,j} = \lambda(i+1)_j - \lambda(i)_j
$$
for $(i,j) = (1,1), (2,1), \dots, (m,1), (2,2),\dots,(m,2),\dots,(m,m)$. The pattern is recorded as a lower-triangular matrix (array of shapes of subtableaux) and the datum is recorded as a sequence.
% 
For example, if 
\[
    \tau = \young(1112,23) 
\]
then
\begin{gather*}
%    \text{if } \tau = \young(1112,23) \text{ then } 
\gt(\tau) = \begin{matrix}
       3 \\
       4 & 1 \\ 
       4 & 2 & 0 
   \end{matrix} \text{ and }
   n_\bullet(\tau) = (1,0,1)\,. 
\end{gather*}
% 
% TODO
% \begin{theorem}(CITE KAM07)
%     Taking $\vi$-Luszig datum is a bijection $P\to\NN^{\ell}$. 
% \end{theorem}
% 
We need the following two results from \cite{dthesis}.
\begin{proposition}
    \label{pr:govsasirrecs}
    The decomposition
    \begin{equation*}
        % \label{eq:govsasirrecs}
        \overline{\OO}^\lambda\cap\TT_\mu\cap\n = \bigsqcup_{\tau\in YT(\lambda)_\mu} X(\tau)
    \end{equation*}
    is\dots
\end{proposition}
% 
Denote by $Z(\tau)\subset\Gr$ the closure of the image of $X(\tau)$ under the isomorphism of \Cref{cor:mvy}. 
\acom{Still need Lusztig data of MV cycles; with it $B(\infty)$, stable vs ordinary, etc?}
\jcom{Do you want $ Z(\tau)$ to be the closure?}
\acom{Sure}

% 
\begin{proposition}
    \label{prop:dth}
    % The isomorphism 
    % $\phi: \overline{\OO}^\lambda\cap\TT_\mu\cap\n \to \overline\Gr^\lambda\cap S^\mu_-$ 
    % is compatible with the decomposition of \Cref{pr:govsasirrecs}
    % the bijection $YT(\lambda)_\mu \to \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ 
    % in the sense that 
    $Z(\tau)$ is dense in the MV cycle whose Lusztig datum is $n_\bullet(\tau)$. 
\end{proposition}
\acom{We would like to use the action of $W$ which gives isomorphisms
$Gr^\lambda \cap Gr_\mu \cap S^\mu \cong Gr^\lambda \cap Gr_{w\mu} \cap S^{w\mu}$ to generalize to non-dominant $\mu$. But the Lusztig datum of $\tau\in YT(\lambda)_\mu$ may not appear as the Lusztig datum of any element of $YT(\lambda)_{w\mu}$..}
% This gives us the dimension of Gr^\lambda \cap Gr_\mu \cap S^\mu.
\begin{lemma}
Alternate description. Works for non-dominant $\mu$. 
$$
Z(\tau) = \{
L\in\Gr : L\cap\CC[t]^i\in\Gr^{\lambda(i)}\cap S^{\mu(i)}\text{ for all }i \}
$$
is an MV cycle. 
\end{lemma}
% Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ (resp.\ $\mu'(i),\mu''(i)$) the shape (resp.\ the weight) of $\tau'(i),\tau''(i)$ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all 
% % but its first $i$ boxes
% boxes of weight exceeding $i$. 
% % If the tableau contains repeated entries then first means leftmost.
% 
\jcom{I don't think that you should mention this partial inverse here.  I think that you should explain here how the generalized orbital varieties are indexed by the tableaux, in other words, how $ X(\tau) $ is defined.}
\acom{Ok, I moved it.}

@@

% 
% In this section we demonstrate how to put the main results of this paper into practice.
% 
% 
In this part we prove that the product 
% the ideal of 
% $Z'\ast_\AA Z''$ 
$b_{Z'}b_{Z''}\in\CC[N]$ can be computed from a ``minimal'' pair $(\tau',\tau'')$ of semistandard Young tableaux for the Lusztig data  $(n_\bullet(Z'),n_\bullet(Z''))$. 
% 
\rcom{I don't think we introduced $\CC[N]$ or the elements $b_Z$ yet. Should I talk about cluster algebras/exchange relations before this?}
To begin, let $\tau',\tau''$ be given and let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
%

% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.} 
Given $s\in\CC$, let 
\begin{equation*}
    X(\tau')\ast_s X(\tau'') = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}\,.
\end{equation*}
% 
% and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
% If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$.
% \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}. Can similarly identify $X'\ast_s X'' = X'\times X''$ by performing the obvious change of basis and block-diagonalizing. May make sense to introduce $\ast_s$ in greater generality, earlier; or at least on MV cycles earlier, since here I should actually make the definition for $Z(\tau)$'s.. which is ok, as in not a loss of generality. Still..}

@@

\begin{proof}
    % We wish to apply \Cref{prop:dth}. Nope
    % We will also need \Cref{le:Grl1l2}. Nope 
    % Consider the following diagram.
    % \[
    % \begin{tikzcd}
    %     X'\ast_s X'' \ar[r,dashed,"?"] \ar[d,"\bar g"] & X'\times X'' \ar[d," \phi\times \phi"] \\ 
    %     \Gr_{0,s}\ar[r,"\tau_s"] & \Gr\times\Gr
    % \end{tikzcd}
    % \]
    % \acom{Not sure what's a good notation for the vertical arrows. Don't want to introduce $\phi$. $\bar g(A) = g(A)\CC[t]^m$ temporarily.}
    % We show that the image of $\tau_s\circ \bar g$ coincides with the image of $\phi\times\phi$ which is dense in $Z'\times Z''$ by \Cref{prop:dth}.
    % % 
    Let $A\in X(\tau')\ast_s X(\tau'')$, let $i = 1,\dots, m$.  
    % Denote by 
    % $E_a$ the generalized $a$-eigenspace of $A$, and by 
    Clearly, the lattices $L=g(A)\CC[t]^m$ and $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ are related by
    $$
    L\cap \CC[t]^i = l. 
    $$
    By definition of $X'\ast_s X''$,  $A\big|_{\CC^{|\mu(i)|}}$ has Jordan type $((\lambda'(i),0),(\lambda''(i),s))$ and lies in $\UU^{\mu'(i),\mu''(i)}_{0,s}$. So, by \Cref{th:OTGrW}, $l\in\Gr_{0,s}^{\lambda'(i),\lambda''(i)}\cap S^{\mu'(i),\mu''(i)}_{0,s}$ which fits the alternate description of $Z(\tau)$..

    \acom{..assuming $\tau_s$ identifies these intersections with products of intersections.}

    \jcom{I removed the $, s)$ from 1.  I don't understand the statement of 2.}
    \acom{Yup, me neither. Getting there..}

    \jcom{I think that it is actually a bit simpler.  Again from teaching algebraic geometry, I found the following.  If $ A $ is a principal ideal domain, then $M $ is flat iff it is torsion-free.}

    \acom{Here $A$ is $\CC[t]$ and $M = \cO$ right? Better, agreed. Does the direction: torsion free implies flat, or not flat implies not torsion free, hold even without the PID assumption? This belongs way back in Joel's Lemma}

    % In particular, we see that 
    % \[
    % Z(\tau) = \{L \in \Gr: L\cap\CC[t]^i \in \Gr^{\lambda(i)} \text{ for } i = 1,\dots, m\}\,.     
    % \]
\end{proof}

\acom{We compute zero fibres of $\ast_s$ by applying the results of \Cref{dthesis}..}

>>>>

On the one hand, if $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $, then $ g(A)$ is lower-triangular with diagonal $ t^{\mu'} (t-s)^{\mu''}$, and so $ g(A) \in N_-[t, t^{-1}, (t-s)^{-1}] t^{\mu'} (t-s)^{\mu''}$. 
% \acom{not $g(A)\CC[t]^m$}
% \jcom{This one isn't a point in $ \Gr$, the others I changed.}

On the other hand, if $ (g(A)\CC[t]^m, s) \in S^{\mu', \mu''}_{0,\AA}$, then we can write 
$$
    g t^\mu r= n t^{\mu'} (t-s)^{\mu''}
$$
for some $ r \in G(\CC[t]), n \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu''} t^{-\mu''}$ which lies in $ T_1(\Oinf) $. % was CC\xt[]
Note that $ h^{-1}n h \in N_-(\Kinf)$, 
% ((t^{-1}))
so we can factor it as $ h^{-1} n h  = n_1 n_2 $, where $ n_1 \in N_{-,1}(\Oinf), n_2 \in N_-(\CC[t])$.  So then after doing a bit of algebra, we reach
$$
    t^\mu r (t^{-\mu} n_2^{-1} t^\mu) t^{-\mu} = g^{-1} h n_1.
$$
Since $ g, h, n_1 \in G_1(\Oinf)$, the right hand side $ g^{-1} h n_1 $ lies in $ G_1(\Oinf) $.  Since $ \mu $ is dominant, $ t^{-\mu} n_2 t^\mu \in N_-(\CC[t])$, and so the left hand side lies in $t^\mu G(\CC[t]) t^{-\mu}$.

Moreover, since $ \mu $ is dominant, we know that 
$$
    t^\mu G(\CC[t]) t^{-\mu} \cap G_1(\Oinf) = N_{-,1}(\Oinf)\,.
$$
% $$t^\mu G(\cO) t^{-\mu} \cap G_1(\CC\xt[t^{-1}]) = N_1(\CC\xt[t^{-1}]\,.$$
Thus, we deduce that $ g^{-1} h n_1 \in N_{-,1}(\Oinf)$ 
% $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ 
and hence $ g(A) \in t^{\mu'} (t-s)^{\mu''}N_{-,1}(\Oinf) $.  
% Given that we know that 
Since $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA}$ as desired.
\end{proof}
% 
% \jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows). To make them correct we should either switch to having $ \mu$ being antidominant or switch $ N$ to $ N_-$.  In this proof $ g(A)$ generally denotes a group element, rather than an affine Grassmannian element which conflicts a bit with earlier usage.}
% 
%\acom{What was the answer to Roger's question why is $g^{-1}hn_1 \in G_1 (\Oinf)$}
% 
%\rcom{So if we look at $g = g(A)t^{-\mu}$, since $A \in \TT_\mu$, the entries of $g(A)_{ij}$ are polynomials of degree $\min(\mu_i-1,\mu_j-1)$ when $i \neq j$, otherwise of degree $\mu_i$. When we multiply by $t^{-\mu}$, we scale the $i$th column by $t^{-\mu_i}$. So the diagonal entries are $1 + p$ where $p \in t^{-1}\CC[t^{-1}]$ while the off-diagonal entries in column $i$ have highest (in $t$) degree $\min(\mu_i-1, \mu_j-1) - \mu_i < 0$. Hence $g \in G_1(\cO_\infty)$.}
%

Restricting to the zero fibre and applying $\tau_0$ we recover \cite[a main result]{dthesis}, itself a corollary of the ordinary affine Grassmannian version of \Cref{th:OGrl}, \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}. 
% 
\begin{corollary}
    \label{cor:mvy}
    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu$. 
\end{corollary}
The irreducible components of the closure of the intersection on the lefthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}. By BKK the set of MV cycles of all possible types and weights can be glued together to form a \textbf{perfect basis} of $\CC[N]$.

\acom{We are ready for applications! One of the motivations for this paper is... Abstractly multiplication is $\ast_s$... To compute we now carry this across \Cref{th:OTGrW}.}

\section{Falling Action} % Resolution
\subsection{MV cycles}
\begin{itemize}
    \item $\overline{A(n_\bullet)}$
    \item $D_\gamma$ 
    \item MV basis?
\end{itemize}
% \acom{Recall (from optional \Cref{s:exposition}) the question motivating this work --- Roger's thesis, cluster monomials and the MV basis. Clarify that whereas we have so far only seen spaces related to ``ordinary MV cycles'' it is the ``stable MV cycles'' that are used to define the MV basis of $\CC[N]$ that the motivating question is concerned with. This discrepancy is the reason we might want to discuss maps $B(\infty)\to B(\lambda)$.}
% 
\begin{comment}
\begin{theorem}
    Let $\lambda_i\ge\mu_i$ be dominant ($i=1,2$), $\mu = \mu' +\mu''$, and $\lambda =\lambda'+\lambda''$. 
    % I have an irrational dislike of ending sentences with subscripts --- can we fix this?
    There is an isomorphism 
    \begin{equation}
        \overline{\OO}_{\lambda',\lambda''}\cap\TT_{\mu',\mu''} \to \overline\Gr_\AA^{\lambda',\lambda''}\cap \cW_{\mu',\mu''}
    \end{equation}
    got by taking a $\mu\times\mu$ block matrix $A$ in the $s$-fibre $\overline{\OO_{\lambda',\lambda''}^s}\cap\TT_{\mu',\mu''}^s$ on the left to the representative of the $s$-fibre on the right defined by  
    \begin{equation}
        \begin{split}
            g &= t^{\mu'} (t-s)^{\mu''} + a(t) \\
            a_{ij}(t) &= - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1}
        \end{split}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
\end{theorem}

@@

\begin{proof}
    % Copy Roger's proof.
    We have
\[
\begin{split}
    S_{\mu_1, \mu_2} & = N\xT[t^{-1}]t^{\mu_1}(t-s)^{\mu_2} \\
     & \subset T_1\xt[t^{-1}] N\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = T_1\xt[t^{-1}] N_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \qquad \text{\cite[Lemma 2.3]{kamnitzer2014yangians}}\\
     & = B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & \subset G_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & = W_{\mu_1 + \mu_2}
\end{split}
\]
where $B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2}$ since 
\[
\frac{t}{t-s} = 
1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
\in B_1\xt[t^{-1}].
\]
\end{proof}
\end{comment}
% 
\subsection{Alternate MV}
We begin this section with some new notation. Let $YT(\lambda)_\mu$ denote the set of (possibly semistandard) Young tableaux of (arbitrary) shape $\lambda$ and (arbitrary) weight $\mu$. Here, the weight of a tableau is a sequence $(\mu_1,\mu_2,\dots)$ recording the number of boxes of weight $i = 1,2,\dots$ that the tableau contains, and the weight of a box is just the number that the box contains.
% For the sake of making a definition, we momentarily put some letters of our alphabet in unexpected roles, and ask you to suspend your disbelief. Given an arbitrary tableau $t$ having weight $w$ and shape $s$, we denote by $s(i)$ (resp.\ $w(i)$) the shape (resp.\ the weight) of $t(i)$, the tableau got from $t$ by discarding all boxes of weight exceeding $i$.

Given $\tau\in YT(\lambda)_\mu$ denote by $\lambda(i)$ (resp.\ $\mu(i)$) the shape (resp.\ the weight) of $\tau(i)$, the tableau got from $\tau$ by discarding all boxes of weight exceeding $i$. 
%

The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is got from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ \acom{cite BZ} by the formula 
$$
n_\bullet(\tau)_{i,j} = \lambda(i+1)_j - \lambda(i)_j
$$
for $(i,j) = (1,1), (2,1), \dots, (m,1), (2,2),\dots,(m,2),\dots,(m,m)$. The pattern is recorded as a lower-triangular matrix (array of shapes of subtableaux) and the datum is recorded as a sequence.
% 
For example, if 
\[
    \tau = \young(1112,23) 
\]
then
\begin{gather*}
%    \text{if } \tau = \young(1112,23) \text{ then } 
\gt(\tau) = \begin{matrix}
       3 \\
       4 & 1 \\ 
       4 & 2 & 0 
   \end{matrix} \text{ and }
   n_\bullet(\tau) = (1,0,1)\,. 
\end{gather*}
% 
This combinatorics is relevant because by work of the third author the MV cycles are parametrized by Lusztig data. (This holds much more generally than the present scope.)
% 
We can associate to $\tau$ an MV cycle. \acom{which is something we haven't introduced yet.} Let 
%  
\begin{equation*}
    Z(\tau) = 
    % \overline{
        \{
            L\in S^\mu : L\cap\CC[t]^i\in\Gr^{\lambda(i)}\text{ for all }i 
        \}\,. 
    % }
\end{equation*}
% 
\begin{proposition}
    \label{pr:newmvdes}
    $\overline{Z(\tau)}$ the MV cycle whose Lusztig datum is $n_\bullet(\tau)$. 
\end{proposition}
% This gives us the dimension of Gr^\lambda \cap Gr_\mu \cap S^\mu.
% Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ (resp.\ $\mu'(i),\mu''(i)$) the shape (resp.\ the weight) of $\tau'(i),\tau''(i)$ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all 
% % but its first $i$ boxes
% boxes of weight exceeding $i$. 
% % If the tableau contains repeated entries then first means leftmost.
% 
% \jcom{I don't think that you should mention this partial inverse here.  I think that you should explain here how the generalized orbital varieties are indexed by the tableaux, in other words, how $ X(\tau) $ is defined.}
% \acom{Ok, I moved it.}

@@

% 
% In this section we demonstrate how to put the main results of this paper into practice.
% 
% 
\subsection{Fusion of MVCs}
Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before, and take $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$. 
%

Given $A \in M_N(\CC)$ we denote by 
% $A\big|_{\CC^i}$ 
$A\big|_{\CC^p}$ 
the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors. If $A\big|_{\CC^p}$ preserves $\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. 
% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.} 
Given $s\in\CC$, let 
\begin{equation*}
    X(\tau')\ast_s X(\tau'') = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}\,.
\end{equation*}
% 
% and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
% If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$.
% \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}. Can similarly identify $X'\ast_s X'' = X'\times X''$ by performing the obvious change of basis and block-diagonalizing. May make sense to introduce $\ast_s$ in greater generality, earlier; or at least on MV cycles earlier, since here I should actually make the definition for $Z(\tau)$'s.. which is ok, as in not a loss of generality. Still..}

@@

\begin{proof}
    % We wish to apply \Cref{prop:dth}. Nope
    % We will also need \Cref{le:Grl1l2}. Nope 
    % Consider the following diagram.
    % \[
    % \begin{tikzcd}
    %     X'\ast_s X'' \ar[r,dashed,"?"] \ar[d,"\bar g"] & X'\times X'' \ar[d," \phi\times \phi"] \\ 
    %     \Gr_{0,s}\ar[r,"\tau_s"] & \Gr\times\Gr
    % \end{tikzcd}
    % \]
    % \acom{Not sure what's a good notation for the vertical arrows. Don't want to introduce $\phi$. $\bar g(A) = g(A)\CC[t]^m$ temporarily.}
    % We show that the image of $\tau_s\circ \bar g$ coincides with the image of $\phi\times\phi$ which is dense in $Z'\times Z''$ by \Cref{prop:dth}.
    % % 
    Let $A\in X(\tau')\ast_s X(\tau'')$, let $i = 1,\dots, m$.  
    % Denote by 
    % $E_a$ the generalized $a$-eigenspace of $A$, and by 
    Clearly, the lattices $L=g(A)\CC[t]^m$ and $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ are related by
    $$
    L\cap \CC[t]^i = l. 
    $$
    By definition of $X'\ast_s X''$,  $A\big|_{\CC^{|\mu(i)|}}$ has Jordan type $((\lambda'(i),0),(\lambda''(i),s))$ and lies in $\UU^{\mu'(i),\mu''(i)}_{0,s}$. So, by \Cref{th:OTGrW}, $l\in\Gr_{0,s}^{\lambda'(i),\lambda''(i)} \cong \Gr^{\lambda'(i)}\times \Gr^{\lambda''(i)}$ so $(l(0),l(s))\in Z(\tau')\times Z(\tau'')$.
\end{proof}
Let $X(\tau')\ast_0 X(\tau'')$ be the zero fibre of $\overline{\cup_{s\in\CC-0} X'\ast_s X''}$. 
\begin{itemize}
    \item $X'\ast_0 X'' \cong Z'\ast_0 Z''$ 
    \item $X'\ast_0 X''$ is a union of GOVs
    \item hence, $Z'\ast_0 Z''$ is a union of associated MVCs
\end{itemize}

What is a GOV? Let $X(\tau)$ be the top-dimensional \acom{speak to this?} irreducible component of
% from $\tau\in YT(\lambda)_\mu$ by 
\[
% X(\tau) = 
% \overline{
    \{
        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
    \}\,. 
% }    
\]
$\overline{X(\tau)}$ is called a \textbf{generalized orbital variety}. 
% 
% By \cite[?]{dthesis}.
\begin{proposition}
    \label{pr:govsasirrecs}
    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{\overline{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
\end{proposition}

\begin{proposition}(\cite{baumann2019mirkovic})
    % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
    Let $Z',Z''$  be MV cycles of type $\lambda',\lambda''$ and weight $\mu',\mu''$ resp.\ and assume that $\lambda',\lambda'',\mu = \mu' + \mu''$ are dominant. 
    Then 
    \begin{equation}
        Z'\ast_0 Z'' = \cup Z(\tau)
        % \label{eq:tabmult}
        % % Z_\tau\ast Z_\sigma 
        % m_{\lambda'\lambda''} ([Z']\otimes[Z'']) 
        % = 
        % % \sum_{Z\in\cZ(\lambda)_\mu} 
        % \sum_{\tau\in S(\lambda)_\mu}
        % i\left(
        %     X(\tau), X(\tau')\circ X(\tau'')
        % \right) [Z(\tau)]\,. 
    \end{equation}
    with $i\left(X(\tau), X(\tau')\circ X(\tau'')\right)$ copies of $Z(\tau)$ showing up on the RHS. 
\end{proposition}
% 
\acom{Closures missing. Here and elsewhere}
